Analyzing Geographic and Demographic Patterns of Homelessness

### 2024-01-25 outputs/paper/paper.qmd
update {#sec-discussion}

To dissect the demographic and geographic patterns within the shelter system in Toronto, spotlighting trends in service utilization and capacity, this paper is organized into the following sections: Data, and Discussion.  In the Data section, I discuss a detailed description of the data source and collection methods. It then progresses to an analysis of demographic and geographic patterns in shelter usage, followed by a discussion on the observed trends and their broader implications. The final sections of the discussion part critically evaluate the study's limitations and propose directions for future research.

@@

# Discussion

>>>>

To dissect the demographic and geographic patterns within the shelter system in Toronto, spotlighting trends in service utilization and capacity, this paper is organized into the following sections: Data (@sec-data), and Discussion (@sec-discussion).  In the Data section, I discuss a detailed description of the data source and collection methods. It then progresses to an analysis of demographic and geographic patterns in shelter usage, followed by a discussion on the observed trends and their broader implications. The final sections of the discussion part critically evaluate the study's limitations and propose directions for future research.

@@

# Discussion {#sec-discussion}
